---
title: "Graphs"
author: "Tyler Clark"
date: "12/15/2019"
output: word_document
---

```{r}
library(tidyverse)
library(ggthemes)
library(ggrepel)
library(tidyquant)
library(scales)
library(lubridate)
# library(xlsx)
library(glue)
```


LPX Orange is #f36e21
    Blue is #005581


```{r}
lpx <- data.frame(year = c(2009:2018),
                  sales = c(1054.7, 1383.6, 1356.9, 1715.8, 2085.2, 1934.8, 1892.5, 2233.4, 2733.9, 2828))
lpx <- lpx %>% 
  mutate(growth = round((lpx$sales - lag(lpx$sales)) / lag(lpx$sales),
                        digits = 3),
         positive = as.factor(if_else(growth > 0, "green", "red")),
         percent_g = str_c(as.character(growth*100), "%"))

```


Original Revenue, no predictions

```{r}
ggplot(lpx) + 
  geom_line(aes(year, sales), 
            color = "#f36e21", 
            size = 2) +
  geom_point(aes(year, sales), 
             color = "#005581", 
             size = 3) +
  ggtitle("Figure 1: Revenue") +
  xlab("Source: LPX") +
  ylab("Revenue ($ mil)") +
  scale_x_continuous(breaks = c(2009:2018)) +
  scale_y_continuous(limits = c(1000,3000),
                     breaks = c(1000,1250,1500,1750,2000,2250,2500,2750,3000)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 17, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_text(hjust = 0,
                                    face = "italic"),
        axis.text.x = element_text(size = 12,
                                   face = "bold"),
        axis.text.y = element_text(size = 12,
                                   face = "bold"),
        panel.grid.minor = element_blank())

```


Attempting to show growth as line

```{r}
ggplot(lpx) +
  geom_col(aes(year, sales)) +
  geom_line(aes(year, growth* 1000 + 1000), size = 2, color = "red")
```



Growth as text

```{r}
# Blue line & title
# Colored dots, black growth text
ggplot(lpx) +
  geom_line(aes(year, sales), 
            color = "#005581", 
            size = 2) +
  geom_point(aes(x = year, y = sales, color = positive), 
             # color = "#005581", 
             size = 4,
             show.legend = FALSE
             ) +
  geom_label(aes(x = year, 
  # geom_text(aes(x = year, # Gets rid of boxes
                 y = sales, 
                 label = growth, 
                 # color = positive
  ),
             vjust = -1,
             show.legend = FALSE) +
  scale_color_manual(values = c("green","red")) +
  ggtitle("Figure 1: Revenue ($ mil)") +
  xlab("Source: LPX") +
  ylab("Revenue ($ mil)") +
  scale_x_continuous(breaks = c(2009:2018)) +
  scale_y_continuous(limits = c(1000,3000),
                     breaks = c(1000,1250,1500,1750,2000,2250,2500,2750,3000)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 17, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_text(hjust = 0,
                                    face = "italic"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 12,
                                   face = "bold"),
        axis.text.y = element_text(size = 12,
                                   face = "bold"),
        panel.grid.minor = element_blank())



# Blue title, blue line
# orange dots, colored text

ggplot(lpx) +
  geom_line(aes(year, sales), 
            color = "#005581", 
            size = 2) +
  geom_point(aes(x = year, y = sales, color = positive), 
             color = "#f36e21",
             size = 3,
             show.legend = FALSE
             ) +
  geom_label(aes(x = year, 
  # geom_text(aes(x = year, # Gets rid of boxes
                 y = sales, 
                 label = growth, 
                 color = positive
  ),
             vjust = -1,
             show.legend = FALSE) +
  scale_color_manual(values = c("springgreen4","red")) +
  ggtitle("Figure 1: Revenue ($ mil)") +
   xlab("Source: LPX") +
  ylab("Revenue ($ mil)") +
  scale_x_continuous(breaks = c(2009:2018)) +
  scale_y_continuous(limits = c(1000,3000),
                     breaks = c(1000,1250,1500,1750,2000,2250,2500,2750,3000)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 17, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_text(hjust = 0,
                                    face = "italic"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 12,
                                   face = "bold"),
        axis.text.y = element_text(size = 12,
                                   face = "bold"),
        panel.grid.minor = element_blank())

ggplot(lpx) +
  geom_line(aes(year, sales), 
            color = "#005581", 
            size = 2) +
  geom_point(aes(x = year, y = sales, color = positive), 
             color = "#f36e21",
             size = 3,
             show.legend = FALSE
             ) +
  geom_label(aes(x = year, 
  # geom_text(aes(x = year, # Gets rid of boxes
                 y = sales, 
                 label = percent_g, 
                 color = positive
  ),
             vjust = -1,
             show.legend = FALSE) +
  scale_color_manual(values = c("springgreen4","red")) +
  ggtitle("Figure 1: Revenue ($ mil)") +
   xlab("Source: LPX") +
  ylab("Revenue ($ mil)") +
  scale_x_continuous(breaks = c(2009:2018)) +
  scale_y_continuous(limits = c(1000,3000),
                     breaks = c(1000,1250,1500,1750,2000,2250,2500,2750,3000)) +
  theme_minimal() +
  theme(plot.title = element_text(size = 17, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_text(hjust = 0,
                                    face = "italic"),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 12,
                                   face = "bold"),
        axis.text.y = element_text(size = 12,
                                   face = "bold"),
        panel.grid.minor = element_blank())

```



Columns instead of lines

```{r}
ggplot(lpx) +
  geom_col(aes(year, sales),  # X and Y axis
           fill = "#f36e21",  # Fill inside of each bar, which is LPX Orange
           color = "#005581", # Outline of each bar, which is LPX Blue
           size = 1) +        # Size of outline 
  geom_label(aes(x = year,    # X axis placement of label
  # geom_text(aes(x = year,   # Set to not run, but would get rid of boxes, leaves only the text
                 y = sales,   # Y axis placement of label
                 label = growth,    # Specify text in label
                 color = positive), # Makes the label different colors
             vjust = -.25,          # Vertical Adjust, Move label up slightly so there is no overlap
             show.legend = FALSE) + # Don't show the legend for the colors
  scale_color_manual(values = c("springgreen4","red")) + # Manually change color of labels to be more readable
  ggtitle("Figure 1: Revenue ($ mil)") + # Set the title of the graph
  xlab("Source: LPX") +                  # X axis title
  ylab("Revenue ($ mil)") +              # Y axis title
  scale_x_continuous(breaks = c(2009:2018)) + # X axis ticks(years), otherwise only labels every 2-3 years
  scale_y_continuous(limits = c(0,3000),      # Y axis shows 0-3000 to have room for highest labels
                     breaks = c(0,500,1000,1500,2000,2500,3000)) + # Y axis ticks(amount), otherwise only labels 1500, 2000, 2500
  theme_minimal() +                                   # Light colored background
  theme(plot.title = element_text(size = 17,          # Make the title bigger
                                  hjust = .5,         # Center the title
                                  face = "bold",      # Bold the title
                                  color = "#005581"), # Make title LPX blue
        axis.title.x = element_text(hjust = 0,        # Make X axis title left aligned
                                    face = "italic"), # Italicize "Source: LPX"
        axis.title.y = element_blank(),               # Get rid of Y axis title because it is repetitive and these will end up being very small graphs
        axis.text.x = element_text(size = 12,         # Make X axis ticks bigger
                                   face = "bold"),    # Bold the X axis years to make more readable
        axis.text.y = element_text(size = 12,         # Make Y axis ticks bigger
                                   face = "bold"),    # Bold Y axis ticks(amount) to make more readable
        panel.grid.minor = element_blank()            # Remove background lines that do not correspond to a tick. Otherwise would have another line in betweeen each.
        )
```



REAL GRAPHS BELOW

Load from OneDrive, get rid of a few empty columns

```{r}
# LPX <- t(IS_BS_CF) %>% data.frame()
# LPX <- LPX[,-c(4,9,10,15,20,24,26,27,31,35)]
```


A. Revenue

```{r}
lpx <- data.frame(Revenue = c(1892.5, 2233.4, 2733.9, 2828,
                              2613.35, 2795.35, 2977.35, 3159.35, 3341.35),
                  Year = c(2015:2023))

lpx <- lpx %>% mutate(growth = round((lpx$Revenue - lag(lpx$Revenue)) / lag(lpx$Revenue),
                                     digits = 3) * 100,
                      positive = as.factor(if_else(growth > 0, "green", "red")))
lpx <- lpx %>% mutate(growth_s = str_c(as.character(growth), "%"))
lpx <- lpx[-1,] # Get rid of 2015


ggplot(lpx) +
  geom_line(aes(Year, Revenue), 
            color = "#005581", 
            size = 2.5) +
  geom_point(aes(x = Year, y = Revenue, color = positive), 
             color = "#f36e21",
             size = 4,
             show.legend = FALSE
             ) +
  geom_label(aes(x = Year, 
                 y = Revenue, 
                 label = growth_s, 
                 color = positive),
             size = 6,
             vjust = 0,
             nudge_y = 90,
             show.legend = FALSE) +
  scale_color_manual(values = c("springgreen4","red")) +
  ggtitle("Figure 11: Revenue") +
  labs(caption = "Source: LPX, Team Assessment") +
  ylab("Millions $") +
  scale_x_continuous(breaks = c(2016:2023)) +
  scale_y_continuous(limits = c(2200,3600),
                     breaks = seq(from = 2000, to = 3500, by = 250)) +
  theme_economist_white() +
  # theme_stata() +
  theme(plot.title = element_text(size = 25, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 18,
                                    face = "bold",
                                    color = "#005581"),
        axis.text.x = element_text(size = 18,
                                   face = "bold"),
        plot.caption = element_text(size = 17, 
                                    hjust = -.25,
                                    vjust = .1,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold")
        )

# ggsave("Graphs/Revenue.png", dpi = 1000)
```


B. Gross vs. Operating vs. Net

```{r}
lpx <- lpx %>% mutate(Gross = c(404.3, 735.8, 744,        
                                687.53, 735.41, 783.29, 831.17, 879.06),
                      Gross_P = c(22.1, 26.91, 26.31,
                                  26.31, 26.31, 26.31, 26.31, 26.31),
                      Operating_Income = c(210.2, 532.8, 526.1,
                                           486.17, 520.03, 553.88, 587.74, 621.6),
                      Operating_Income_P = c(9.41, 19.49, 18.6,
                                             18.6, 18.6, 18.6, 18.6, 18.6),
                      Net_Income = c(149.8, 389.8, 394.6,
                                     378.13, 399.44, 419.33, 437.61, 454.1),
                      Net_Income_P = c(6.71, 14.26, 13.95,
                                       14.47, 14.29, 14.08, 13.85, 13.59)
                      )
Margin <- NA
Year <- NA
for(i in 1:nrow(lpx)) {
  Margin <- c(Margin, lpx$Gross_P[i], lpx$Operating_Income_P[i], lpx$Net_Income_P[i])
  Year <- c(Year, rep(lpx$Year[i],3))
}
Margin <- na.omit(Margin)
Year <- na.omit(Year)

lpx_b <- data.frame(Margin,
                    margin_type = rep(c("Gross","Operating","Net"), 8),
                    Year)

lpx_b <- lpx_b %>% mutate(Margin = Margin / 100)

lpx_b <- lpx_b %>% filter(Year <= 2020)

ggplot(lpx_b) + 
  geom_col(aes(x = Year,
               y = Margin,
               fill = as.factor(margin_type)),
           position = "dodge",
           stat = "identity",
           width = .7)  +
  ggtitle("Figure 12: Gross, Operating and Net Margins") +
  labs(caption = "Source: LPX, Team Assessment") +
  scale_x_continuous(breaks = c(2016:2023)) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1),
                     breaks = c(0,.05,.1,.15,.2,.25,.3)) +
  scale_fill_manual(values = c("#f36e21","#005581","#a3039c"), 
                    labels = c("Gross Margin", "Operating Margin", "Net Margin")) +
  theme_economist_white() +
  # theme_stata() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .6, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18,
                                   face = "bold"),
        plot.caption = element_text(size = 18, 
                                    hjust = -.2,
                                    vjust = .1,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold"),
        legend.title = element_blank(),
        legend.spacing.x = unit(.4, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "bottom",
        legend.text = element_text(size = 17)
        )

# ggsave("Graphs/Gross_Operating_Net.png", dpi = 1000)
```


C. a) Revenue Segment donut graph

```{r}
Segment <- data.frame(Segment = c(942.3,160.8,1305.2,390.9,28.8),
                      Name = c("Siding", "SA", "OSB", "EWP", "Other"))

Segment <- Segment %>% mutate(fraction = Segment / sum(Segment))
Segment$ymax <- cumsum(Segment$fraction)
Segment$ymin <-  c(0, head(Segment$ymax, n=-1))
Segment$labelPosition <- (Segment$ymax + Segment$ymin) / 2
Segment$label <- paste0(Segment$Name, "\n value: ", Segment$Segment)

ggplot(Segment, aes(ymax = ymax,
                    ymin = ymin,
                    xmax = 4,
                    xmin = 2,
                    fill = Name)) +
  geom_rect() +
  # geom_label(x = 2,
  #           aes(y = labelPosition,
  #                label = label,
  #                color = Name),
  #           size = 4) +
  ####### DONT TOUCH THESE. IT ONLY GETS WORSE. 2.4, 2.6, 2.5, 2.5, 2.9
  geom_text_repel(aes(x = case_when(Name == "SA" ~ 2.4,
                                    Name == "Siding" ~ 2.6,
                                    Name == "Other" ~ 2.5,
                                    Name == "EWP" ~ 2.5,
                                    Name == "OSB" ~ 2.9,
                                    TRUE ~ 2),
                      y = labelPosition,
                      label = Name,
                      size = 12,
                      fontface = "bold")) +
  scale_fill_brewer(palette = 5) +
  # scale_color_brewer(palette = 5) +
  coord_polar(theta="y") +
  xlim(c(1, 4)) +
  theme_void() +
  ggtitle("Figure 3: Business Segments") +
  labs(caption = "Source: LPX") +
  theme(legend.position = "none",
        plot.title = element_text(size = 17, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        # axis.title.x = element_blank(),
        # axis.title.y = element_blank(),
        # axis.text.x = element_text(size = 12,
        #                            face = "bold"),
        plot.caption = element_text(size = 12, 
                                    hjust = 0,
                                    face = "italic")
        )



Segment <- data.frame(Segment = c(942.3,160.8,1305.2,28.8,390.9),
                      Name = c("Siding", "SA", "OSB", "Other", "EWP"))

Segment <- Segment %>% mutate(fraction = Segment / sum(Segment))
Segment$ymax <- cumsum(Segment$fraction)
Segment$ymin <-  c(0, head(Segment$ymax, n=-1))
Segment$labelPosition <- (Segment$ymax + Segment$ymin) / 2
Segment$label <- paste0(Segment$Name, "\n value: ", Segment$Segment)

ggplot(Segment, aes(ymax = ymax,
                    ymin = ymin,
                    xmax = 4,
                    xmin = 3.5,
                    fill = Name)) +
  geom_rect() +
  # geom_label(x = 2,
  #           aes(y = labelPosition,
  #                label = label,
  #                color = Name),
  #           size = 4) +
  ####### DONT TOUCH THESE. IT ONLY GETS WORSE. 2.4, 2.6, 2.5, 2.5, 2.9
  geom_text_repel(aes(x = case_when(Name == "SA" ~ 3,
                                    Name == "Siding" ~ 2.8,
                                    Name == "Other" ~ 2.86,
                                    Name == "EWP" ~ 3.09,
                                    Name == "OSB" ~ 2.84,
                                    TRUE ~ 2),
                      y = labelPosition,
                      label = Name,
                      size = 12,
                      fontface = "bold")) +
  scale_fill_brewer(palette = 5) +
  # scale_color_brewer(palette = 5) +
  coord_polar(theta="y") +
  xlim(c(1, 4)) +
  theme_void() +
  ggtitle("Business Segments") +
  labs(caption = "Source: LPX") +
  theme(legend.position = "none",
        plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        # axis.title.x = element_blank(),
        # axis.title.y = element_blank(),
        # axis.text.x = element_text(size = 12,
        #                            face = "bold"),
        plot.caption = element_text(size = 18, 
                                    hjust = 0,
                                    face = "italic")
        )

# ggsave("Graphs/Donut.png", dpi = 1000)
```


C. b) Revenue Segment bar graph yearly

```{r}
Segment_bar <- data.frame(Year = c(rep(2018, 5), rep(2017, 5), rep(2016, 5), rep(2015, 5)),
                          Segment = rep(c("Siding", "OSB", "EWP", "SA", "Other"), 4),
                          Revenue = c(942.3, 1305.2, 390.9, 160.8, 28.9, 
                                      884.0, 1302.5, 365.9, 155.3, 30.0,
                                      752.3, 1027.7, 296.9, 136.9, 26.9,
                                      636.4, 807.5, 286.1, 134.9, 29.0))

Segment_bar$Segment <- reorder(Segment_bar$Segment, Segment_bar$Revenue, FUN = mean) 

ggplot(Segment_bar) +
  geom_col(aes(x = Year, y = Revenue, fill = Segment)) +
  ggtitle("Revenue by Business Segment") +
  labs(caption = "Source: LPX") +
  scale_y_continuous(limits = c(0, 3000),
                     breaks = c(0, 1000, 2000, 3000)) +
  scale_fill_manual(values = c("#5dade2", "#2ecc71", "#a3039c", "#005581", "#f36e21")) +
                               #Other      SA         EWP        Siding     OSB
  guides(fill = guide_legend(reverse = TRUE)) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18,
                                   face = "bold"),
        plot.caption = element_text(size = 17, 
                                    hjust = -.1,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold"),
        legend.title = element_blank(),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "bottom",
        legend.text = element_text(size = 17)
        )

# ggsave("Graphs/Revenue_by_Segment.png", dpi = 1000)
```



D. Year to date stock price
Find a stock you want to use for a candlestick graph from NASDAQ and load it in here
```{r}
# stock <- read.csv("HistoricalQuotes.csv", stringsAsFactors = FALSE)
# stock <- stock %>% mutate(Close = as.numeric(str_extract(Close.Last, "[0-9]+.[0-9]+")),
#                           Open = as.numeric(str_extract(Open, "[0-9]+.[0-9]+")),
#                           High = as.numeric(str_extract(High, "[0-9]+.[0-9]+")),
#                           Low = as.numeric(str_extract(Low, "[0-9]+.[0-9]+")),
#                           Date = mdy(Date))
# stock <- stock %>% mutate(diff = Close - Open,
#                           diff_positve = if_else(diff > 0, 1, 0))


# ggplot(stock) + 
#   geom_point(aes(Date, Volume))
# 
# ggplot(stock) + 
#   geom_point(aes(Date, Open)) +
#   geom_point(aes(Date, Close))
# 
# ggplot(stock) +
#   geom_candlestick(aes(x = Date,
#                        y = Close,
#                        open = Open,
#                        high = High, 
#                        close = Close,
#                        low = Low),
#                    colour_up = "green",
#                    colour_down = "red",
#                    fill_up = "green",
#                    fill_down = "red") +
#   ggtitle("Figure 13: YTD Stock Price") +
#   labs(caption = "Source: NASDAQ") + 
#   scale_y_continuous(breaks = c(seq(from = 24, to = 33, by = 3)),
#                      labels = scales::dollar) +
#   scale_x_date(date_breaks = "1 months", 
#                date_labels = "%B") +
#   theme_economist_white() +
#   theme(plot.title = element_text(size = 22, 
#                                   hjust = .5, 
#                                   face = "bold",
#                                   color = "#005581"),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 18,
#                                    face = "bold",
#                                    angle = 45,
#                                    vjust = .9,
#                                    hjust = .9),
#         plot.caption = element_text(size = 17, 
#                                     hjust = -.08,
#                                     face = "italic"),
#         axis.text.y = element_text(size = 17,
#                                    face = "bold")
#         )

# ggsave("Graphs/YTD_Stock_Price.png", dpi = 1000)
```


E. 2019 Q3 Competitors P/E Ratio Comparison

```{r}
Competitors <- data.frame(Company = c("LPX", "Weyerhaeuser", "Potlatch", "West Fraser", "Norbord"),
                          Price =   c(24.58,  27.70,         41.09,      53,            23.95),
                          EPS =     c(.48,    -.21,          .68,        -1.31,         -0.68),
                          PE =      c(51.21,  0.00,          60.42,      0,             0.00),
                          SPS =     c(18.15,  8.87,          12.72,      72.12,         22.34),
                          PS =      c(1.35,   3.12,          3.23,       .735,          1.07),
                          BVPS =    c(10.33,  11.54,         18.38,      37.59,         8.58),
                          PB =      c(2.38,   2.40,          2.23,       1.41,          2.79),
                          FCFPS =   c(0.18,   1.71,          3.87,       -4.62,         -0.17),
                          PFCF =    c(135.43, 16.22,         10.62,      11.96,         0.00))

Comp <- data.frame(Company = c(rep(as.character(Competitors$Company[1]), 9), 
                               rep(as.character(Competitors$Company[2]), 9), 
                               rep(as.character(Competitors$Company[3]), 9), 
                               rep(as.character(Competitors$Company[4]), 9),
                               rep(as.character(Competitors$Company[5]), 9)),
                   Statistic = rep(colnames(Competitors[,2:10]), 5),
                   Value = c(as.vector(unlist(Competitors[1,2:10])), 
                             as.vector(unlist(Competitors[2,2:10])), 
                             as.vector(unlist(Competitors[3,2:10])), 
                             as.vector(unlist(Competitors[4,2:10])), 
                             as.vector(unlist(Competitors[5,2:10]))))

Comp$Company <- factor(Comp$Company, levels = c("LPX", "Potlatch", "West Fraser", "Weyerhaeuser", "Norbord"))

Comp <- Comp %>% mutate(Value = round(Comp$Value, digits = 2))

ggplot(Comp) + 
  geom_col(aes(x = Company,
               y = Value,
               fill = as.factor(Statistic)),
           position = "dodge",
           stat = "identity",
           width = .7)



Comp_A <- Comp %>% filter(Statistic %in% c("PE", "PS", "PB", "PFCF"))
ggplot(Comp_A) + 
  geom_col(aes(x = Company,
               y = Value,
               fill = as.factor(Statistic)),
           position = "dodge",
           # stat = "identity",
           width = .8) +
  ggtitle("2018 Industry Comparison Ratios") +
  labs(caption = "Source: Macrotrends, YCharts") + 
  scale_y_continuous(limits = c(0,140),
                     breaks = c(seq(from = 0, to = 140, by = 20))) +
  scale_fill_manual(values = c("#a3039c", "#005581", "#f36e21", "#2ecc71")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        plot.background = element_rect(size = c(500,300)),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18,
                                   face = "bold",
                                   angle = 20,
                                   vjust = .9,
                                   hjust = .9),
        plot.caption = element_text(size = 17, 
                                    hjust = -.15,
                                    face = "italic"),
        axis.text.y = element_text(size = 17,
                                   face = "bold"),
        legend.title = element_blank(),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = c(.6, .77),
        legend.direction = "horizontal",
        legend.background = element_rect(fill = NA),
        legend.text = element_text(size = 17)
        )

# ggsave("Graphs/Industry_Ratios.png", dpi = 1000)

Comp_B <- Comp %>% filter(Statistic %in% c("EPS", "SPS", "BVPS", "FCFPS"))
Comp_B$Company <- factor(Comp_B$Company, levels = c("LPX", "Norbord", "West Fraser", "Potlatch", "Weyerhaeuser"))
Comp_B$Statistic <- factor(Comp_B$Statistic, levels = c("BVPS", "SPS", "FCFPS", "EPS"))
ggplot(Comp_B) + 
  geom_col(aes(x = Company,
               y = Value,
               fill = as.factor(Statistic)),
           position = "dodge",
           stat = "identity",
           width = .8) +
  ggtitle("2018 Per-Share Competitor Ratios") +
  labs(caption = "Source: Macrotrends, YCharts") +
  scale_y_continuous(limits = c(-5, 73), 
                    breaks = c(seq(from = 0, to = 70, by = 10))) +
  scale_fill_manual(values = c("#005581", "#f36e21", "#a3039c", "#2ecc71")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        plot.background = element_rect(size = c(1,1)),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18,
                                   face = "bold",
                                   angle = 20,
                                   hjust = 1,
                                   vjust = 1),
        plot.caption = element_text(size = 17, 
                                    hjust = -.1,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold"),
        legend.title = element_blank(),
        # legend.spacing.x = unit(.5, "cm"),
        # legend.spacing.y = unit(.6, "cm"),
        legend.key.size = unit(.9, "cm"),
        legend.position = c(.15,.7),
        legend.direction = "vertical",
        legend.text = element_text(size = 17),
        legend.background = element_rect(fill = "white")
        )

# ggsave("Graphs/Industry_Per_Share_Ratios.png", dpi = 1000)
```


F. Siding Segment Revenue by Quarter

```{r}
SS <- data.frame(Quarter = c("'19 Q3", "'19 Q2", "'19 Q1", "'18 Q4", "'18 Q3", "'18 Q2", "'18 Q1"),
                 SS_Strand = c(213, 200, 187, 178, 188, 194, 165),
                 SS_Fiber = c(28, 25, 26, 22, 30, 28, 26),
                 CanExel = c(15, 7, 17, 3, 7, 13, 14)) %>% 
  mutate(SS_Siding = SS_Strand + SS_Fiber)

SS_A <- data.frame(Quarter = rep(SS$Quarter, 2),
                   SmartSiding = c(SS$SS_Strand, SS$SS_Fiber),
                   Type = c(rep("Strand", 7), rep("Fiber", 7)))

ggplot(SS) +
  geom_point(aes(x = Quarter, y = SS_Strand)) +
  geom_point(aes(x = Quarter, y = SS_Fiber)) +
  geom_point(aes(x = Quarter, y = CanExel)) +
  geom_point(aes(x = Quarter, y = SS_Siding))

ggplot(SS) + 
  geom_col(aes(x = Quarter, y = SS_Siding))


# library(scales) # must have for oob = rescale_none
ggplot(SS_A) + 
  geom_col(aes(x = Quarter, y = SmartSiding, fill = Type)) +
  ggtitle("Revenue From SmartSiding") +
  labs(caption = "Source: LPX") +
  scale_fill_manual(values = c("#f36e21", "#005581")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 18,
                                   face = "bold"),
        plot.caption = element_text(size = 17, 
                                    hjust = -.1,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold"),
        legend.title = element_text(size = 17,
                                    face = "bold",
                                    vjust = 1),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "bottom",
        legend.text = element_text(size = 17),
        # legend.box.background = element_rect(fill = "white")
        legend.background = element_rect(fill = "white")
        )

# ggsave("Graphs/Revenue_SmartSiding.png", dpi = 1000)
```


G. Single-Family Housing Starts Quarterly, Freddie Mac Predictions

Explanation of different housing types from US Census Bureau
https://www.census.gov/construction/nrc/nrcdatarelationships.html 

```{r}
Housing_Starts <- data.frame(Single_Family = c(0.89, 0.89, 0.88, 0.83,
                                               0.86, 0.84, 0.88, 0.89,
                                               0.90, 0.93, 0.96, 0.98), # Millions of housing units;
                                                                        # quarterly averages of monthly, seasonally-adjusted levels (reported at an annual rate).
                             Multifamily = c(0.43, 0.37, 0.36, 0.36,
                                             0.35, 0.42, 0.38, 0.38,
                                             0.37, 0.35, 0.32, 0.31),
                             Quarter = c("'18 Q1", "'18 Q2", "'18 Q3", "'18 Q4",
                                         "'19 Q1", "'19 Q2", "'19 Q3", "'19 Q4",
                                         "'20 Q1", "'20 Q2", "'20 Q3", "'20 Q4"))

ggplot(Housing_Starts) +
  geom_line(aes(x = Quarter, y = Single_Family, group = 1),
            color = "#005581",
            size = 2.5) +
  geom_point(aes(x = Quarter, y = Single_Family),
             color = "#f36e21",
             size = 4) +
  ggtitle("Single-Family Housing Starts") +
  ylab("Millions of Homes") +
  labs(caption = "Source: Freddie Mac") +
  scale_y_continuous(limits = c(.82, 1),
                     breaks = c(.85, .9, .95, 1)) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 18,
                                    face = "bold",
                                    color = "#005581"),
        axis.text.x = element_text(size = 14,
                                   face = "bold",
                                   angle = 50,
                                   vjust = 1.1,
                                   hjust = 1),
        plot.caption = element_text(size = 17, 
                                    hjust = -.2,
                                    face = "italic"),
        axis.text.y = element_text(size = 14,
                                   face = "bold"),
        legend.title = element_text(size = 14,
                                    face = "bold"),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "none"
        )

# ggsave("Graphs/Single_Family_Starts.png", dpi = 1000)
```


H. Multifamily Housing Starts Quarterly, Freddie Mac Predictions

Notice the decrease in Multifamily. Following explanation from https://www.investopedia.com/terms/h/housingstarts.asp
"For example, if housing starts show a decline in new single-family units in favor of multifamily housing starts, it could indicate that a supply shortage is looming for single-family housing. That may lead to price increases for that segment, making those units more of a premium. It could also indicate that the general public is shying away from more expensive homes in favor of seeking more affordable multifamily units."

```{r}
ggplot(Housing_Starts) +
  geom_line(aes(x = Quarter, y = Multifamily, group = 1),
            color = "#005581",
            size = 2.5) +
  geom_point(aes(x = Quarter, y = Multifamily),
             color = "#f36e21",
             size = 4) +
  ggtitle("Figure 6: Multifamily Housing Starts") +
  ylab("Millions of Homes") +
  labs(caption = "Source: Freddie Mac") +
  scale_y_continuous(limits = c(.3, .45),
                     breaks = c(seq(from = .3, to = .45, by = .05))) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 18,
                                    face = "bold",
                                    color = "#005581"),
        axis.text.x = element_text(size = 14,
                                   face = "bold",
                                   angle = 50,
                                   vjust = 1.1,
                                   hjust = 1),
        plot.caption = element_text(size = 17, 
                                    hjust = -.2,
                                    face = "italic"),
        axis.text.y = element_text(size = 14,
                                   face = "bold"),
        legend.title = element_text(size = 14,
                                    face = "bold"),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "none"
        )

# ggsave("Graphs/Multifamily_Starts.png", dpi = 1000)
```


I. Single and Multi family starts Quarterly

```{r}
FM <- data.frame(Quarter = rep(Housing_Starts$Quarter, 2),
                 Starts = c(Housing_Starts$Single_Family, Housing_Starts$Multifamily),
                 Type = c(rep("Single-Family", 12), rep("Multifamily", 12)))

Housing_Starts %>% mutate(Total = Single_Family + Multifamily,
                          diff = Single_Family - Multifamily)

ggplot(FM) +
  geom_col(aes(x = Quarter, y = Starts, fill = Type)) +
  ggtitle("Figure 10: Forecasted Housing Starts") +
  ylab("Housing Starts (Millions)") +
  labs(caption = "Source: Freddie Mac")
```


J. Freddie Mac single multi family housing starts difference quarterly and annually

```{r}
HS_Difference <- Housing_Starts %>% mutate(Total = Single_Family + Multifamily,
                                           diff = Single_Family - Multifamily)

ggplot(HS_Difference) +
  geom_col(aes(x = Quarter, y = diff))

ggplot(HS_Difference) +
  geom_point(aes(x = Quarter, y = Single_Family)) +
  geom_point(aes(x = Quarter, y = Multifamily))

HS_Difference <- HS_Difference %>% mutate(growth = if_else(diff > lag(HS_Difference$diff), "springgreen4", "red")) %>% filter(Quarter != "'18 Q1")

ggplot(HS_Difference) + 
  geom_segment(aes(x = Quarter, xend = Quarter, 
                   y = Multifamily, yend = Single_Family,
                   color = growth),
               alpha = .7,
               size = 5) +
  scale_color_manual(values = c("#e74c3c", "springgreen4")) +
  geom_point(aes(x = Quarter, y = Single_Family),
             size = 4.5,
             color = "#005581") +
  geom_point(aes(x = Quarter, y = Multifamily),
             size = 4.5,
             color = "#005581") +
  ggtitle("Figure 5: Difference Between Single, \nMultifamily Housing Starts") +
  ylab("Millions") +
  labs(caption = "Source: Freddie Mac") +
  theme_economist_white() +
  theme(plot.title = element_text(size = 20, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 15,
                                    face = "bold",
                                    color = "#005581"),
        axis.text.x = element_text(size = 14,
                                   face = "bold",
                                   angle = 50,
                                   vjust = 1.1,
                                   hjust = 1),
        plot.caption = element_text(size = 14, 
                                    hjust = -.15,
                                    face = "italic"),
        axis.text.y = element_text(size = 14,
                                   face = "bold"),
        legend.title = element_text(size = 14,
                                    face = "bold"),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "none"
        )

# ggsave("Graphs/FM_Single_Multi.png", dpi = 1000)

Annual <- data.frame(Year = c(2017:2020),
                     Single_Family = c(0.85, 0.87, 0.87, 0.94),
                     Multifamily = c(0.35, 0.38, 0.38, 0.34))

Annual <- Annual %>% mutate(Total = Single_Family + Multifamily,
                            Difference = Single_Family - Multifamily)

Annual_A <- data.frame(Year = rep(Annual$Year, 2),
                       Starts = c(Annual$Single_Family, Annual$Multifamily),
                       Type = c(rep("Single-Family", 4), rep("Multifamily", 4)))

ggplot(Annual) +
  geom_point(aes(x = Year, y = Single_Family)) +
  geom_point(aes(x = Year, y = Multifamily))

ggplot(Annual) +
  geom_col(aes(x = Year, y = Difference))

ggplot(Annual_A) +
  geom_col(aes(x = Year, y = Starts, fill = Type))
```


J. HousingEconomics Predictions. I believe these are the correct numbers. Freddie mac seems too high

```{r}
HE <- data.frame(Year = c(2015:2021),
                 Single = c(713, 785, 852, 873, 869, 902, 917),
                 Multi = c(394, 393, 356, 377, 374, 384, 399))
HE %>% mutate(Single_Percent = Single / (Single + Multi))

HE_A <- data.frame(Year = c(rep(HE$Year, 2)),
                   Type = c(rep("Single-Family", 7), rep("Multifamily", 7)),
                   Houses = c(HE$Single, HE$Multi))

ggplot(HE_A) +
  geom_col(aes(x = Year, y = Houses, fill = Type)) +
  ggtitle("Forecasted Housing Starts") +
  ylab("Housing Starts (Thousands)") +
  labs(caption = "Source: HousingEconomics") +
  scale_y_continuous(limits = c(0, 1350),
                     breaks = c(seq(from = 0, to = 1250, by = 250))) +
  scale_x_continuous(breaks = c(2015:2021)) +
  scale_fill_manual(values = c("#f36e21", "#005581")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 17,
                                    face = "bold",
                                    color = "#005581",
                                    hjust = .2),
        axis.text.x = element_text(size = 17,
                                   face = "bold"),
        plot.caption = element_text(size = 17, 
                                    hjust = -.25,
                                    face = "italic"),
        axis.text.y = element_text(size = 15,
                                   face = "bold"),
        legend.title = element_blank(),
        legend.key.size = unit(.6, "cm"),
        legend.text = element_text(size = 17),
        legend.position = "bottom",
        legend.spacing.x = unit(.5, "cm"),
        )

# ggsave("Graphs/HE_Forecasted_Housing_Starts.png", dpi = 1000)
```



K. 30 Year PMMS (Primary Mortgage Market Survey)

```{r}
# Quarterly average of monthly interest rates (not seasonally-adjusted); reported as an annual rate
PMMS <- data.frame(Rate = c(4.3, 4.5, 4.6, 4.8,
                            4.4, 4.0, 3.7, 3.7,
                            3.8, 3.8, 3.8, 3.8,
                            3.8, 3.8, 3.8, 3.9),
                   Quarter = c("'18 Q1", "'18 Q2", "'18 Q3", "'18 Q4",
                               "'19 Q1", "'19 Q2", "'19 Q3", "'19 Q4",
                               "'20 Q1", "'20 Q2", "'20 Q3", "'20 Q4",
                               "'21 Q1", "'21 Q2", "'21 Q3", "'21 Q4"))

PMMS <- PMMS %>% mutate(Rate = Rate / 100)

ggplot(PMMS) +
  geom_line(aes(x = Quarter, y = Rate, group = 1),
            color = "#005581",
            size = 2.5) +
  geom_point(aes(x = Quarter, y = Rate),
             color = "#f36e21",
             size = 4) +
  ggtitle("30-Year PMMS Interest Rates") +
  labs(caption = "Source: Freddie Mac") +
  scale_y_continuous(breaks = c(seq(from = .037, to = .049, by = .002)),
                     labels = scales::percent_format(accuracy = .1),
                     limits = c(.0365, .049)) +
  scale_x_discrete(labels = c("'18 Q1", "'19 Q1", "'20 Q1", "'21 Q1", "'21 Q4"),
                   breaks = c("'18 Q1", "'19 Q1", "'20 Q1", "'21 Q1", "'21 Q4")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        axis.text.x = element_text(size = 16,
                                   face = "bold"),
                                   # angle = 50,
                                   # vjust = 1.1),
                                   # hjust = 1),
        plot.caption = element_text(size = 16, 
                                    hjust = -.15,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold"),
        legend.title = element_text(size = 18,
                                    face = "bold"),
        legend.spacing.x = unit(.5, "cm"),
        legend.key.size = unit(.5, "cm"),
        legend.position = "none"
        )

# ggsave("Graphs/FM_PMMS.png", dpi = 1000)
```



Came from US Bureau of labor statistics
```{r}
# OSB <- read.csv("WPU09220124.csv")
# OSB <- OSB %>% mutate(date = ymd(DATE))
# 
# ggplot(OSB) +
#   geom_line(aes(x = date, 
#                 y =  WPU09220124, 
#                 group = 1),
#             color = "#005581",
#             size = 2) +
#   ggtitle("Figure 3: Producer Price Index For OSB,\n Waferboard, Pulp, Paper") +
#   labs(caption = "Source: U.S. Bureau of Labor Statistics") +
#   scale_x_date(date_breaks = "2 years", 
#                date_labels = "%Y") +
#   scale_y_continuous(breaks = seq(100, 300, 50),
#                      limits = c(100, 300)) +
#   theme_economist_white() +
#   theme(plot.title = element_text(size = 22, 
#                                   hjust = .5, 
#                                   face = "bold",
#                                   color = "#005581"),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 16,
#                                    face = "bold"),
#         plot.caption = element_text(size = 16, 
#                                     hjust = -.2,
#                                     face = "italic"),
#         axis.text.y = element_text(size = 18,
#                                    face = "bold"),
#         legend.title = element_text(size = 18,
#                                     face = "bold"),
#         legend.spacing.x = unit(.5, "cm"),
#         legend.key.size = unit(.5, "cm"),
#         legend.position = "none"
#         )

# ggsave("Graphs/PPI_OSB.png", dpi = 1000)
```


```{r}
# Wood_Product <- readxl::read_excel("Wood_Product_Manufact.xlsx")
# Wood_Product <- Wood_Product[10:21,]
# colnames(Wood_Product) <- Wood_Product[1,]
# Wood_Product <- Wood_Product[-1,]
# 
# Wood_Product_Date <- vector(length = 11 * 12)
# value <- c(length = 11 * 12)
# k <- 1
# 
# for(i in 1:11) {
#   for(j in 2:13) {
#     value[k] <- Wood_Product[[i,j]]
#     k <- k + 1
#   }
# }
# # value
# value <- as.numeric(value)
# 
# Wood_Product_Date <- rep(as.Date('2009-01-01'), 132)
# 
# for(i in 2:132) {
#   month(Wood_Product_Date[i]) <- month(Wood_Product_Date[i-1]) + 1
#   year(Wood_Product_Date[i:132]) <- year(Wood_Product_Date[i])
# }
# Wood_Product_Date
# 
# Wood_Product <- data.frame(Date = Wood_Product_Date,
#                            PPI = value)
# 
# ggplot(Wood_Product) +
#   geom_line(aes(x = Date, 
#                 y = PPI, 
#                 group = 1),
#             color = "#005581",
#             size = 2) +
#   ggtitle("Figure 4: PPI For Wood Product Manufacturing") +
#   labs(caption = "Source: U.S. Bureau of Labor Statistics") +
#   scale_x_date(date_breaks = "2 years", 
#                date_labels = "%Y") +
#   theme_economist_white() +
#   theme(plot.title = element_text(size = 20, 
#                                   hjust = .5, 
#                                   face = "bold",
#                                   color = "#005581"),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 16,
#                                    face = "bold"),
#         plot.caption = element_text(size = 16, 
#                                     hjust = -.2,
#                                     face = "italic"),
#         axis.text.y = element_text(size = 18,
#                                    face = "bold"),
#         legend.title = element_text(size = 18,
#                                     face = "bold"),
#         legend.spacing.x = unit(.5, "cm"),
#         legend.key.size = unit(.5, "cm"),
#         legend.position = "none"
#         )
# 
# ggsave("Graphs/PPI_Lumber.png", dpi = 1000)

```


Manufacturing stuff Adom sent me

```{r}
Manufacture <- data.frame(Year = c(rep("2017", 3), rep("2018", 3)),
                          Type = rep(c("SA", "Siding", "OSB"), 2),
                          Amount = c(680, 1760, 4895, 750, 2015, 4515))

ggplot(Manufacture) +
  geom_col(aes(x = Year, y = Amount, fill = Type))

ggplot(Manufacture) +
  geom_line(aes(x = Year, y = Amount, color = Type, group = Type), size = 2)

Manufacture$Type <- factor(Manufacture$Type, levels = c("OSB", "Siding", "SA"))

ggplot(Manufacture) +
  geom_col(aes(x = Year, 
               y = Amount, 
               fill = Type), 
           position = "dodge",
           width = .8) +
  ggtitle("Figure 14: Yearly Segment Manufacturing Amounts") +
  ylab("Units Manufactured") +
  labs(caption = "Source: LPX") +
  scale_y_continuous(limits = c(0, 5000), 
                    breaks = c(seq(from = 0, to = 5000, by = 1000))) +
  scale_fill_manual(values = c("#005581", "#f36e21", "#a3039c")) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 19, 
                                  hjust = 1, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.x = element_blank(),
        axis.title.y = element_text(size = 17,
                                    face = "bold",
                                    color = "#005581"),
        axis.text.x = element_text(size = 16,
                                   face = "bold"),
        plot.caption = element_text(size = 16, 
                                    hjust = -.15,
                                    face = "italic"),
        axis.text.y = element_text(size = 16,
                                   face = "bold"),
        legend.title = element_blank(),
        # legend.spacing.x = unit(.5, "cm"),
        # legend.spacing.y = unit(.6, "cm"),
        # legend.key.size = unit(.6, "cm"),
        legend.position = c(.85,.7),
        # legend.direction = "vertical",
        legend.text = element_text(size = 17),
        legend.background = element_rect(fill = "white")
        )

# ggsave("Graphs/Manufacture_Amounts.png", dpi = 1000)

```



```{r}
Export <- data.frame(PPI = c(100.4, 102.6, 103.8,	104.2, 104.4,	104.6, 104.1,	103.4, 102.7,	101.5, 101.8,	101.5, 
                             102.5, 103.2,	100.8, 100.4, 99.3,	97.8,	97.3,	96.3,	95.8,	94.8,	94.1,	93.8), 
                     Date = c(glue("1.{1:12}.18"), glue("1.{1:12}.19")))

Export <- Export %>% mutate(Date = dmy(Date))

ggplot(Export) +
  geom_line(aes(x = Date, 
                y =  PPI, 
                group = 1),
            color = "#005581",
            size = 2) +
  ggtitle("Figure 15: Monthly Export Price Index\nWood Product Manufacturing") +
  ylab("Price Index") +
  labs(caption = "Source: U.S. Bureau of Labor Statistics") +
  scale_x_date(date_breaks = "4 months", 
               date_labels = "%m-%Y") +
  scale_y_continuous(limits = c(93,105),
                   breaks = c(seq(93, 105, 3))) +
  theme_economist_white() +
  theme(plot.title = element_text(size = 22, 
                                  hjust = .5, 
                                  face = "bold",
                                  color = "#005581"),
        axis.title.y = element_text(size = 18,
                                    face = "bold",
                                    color = "#005581"),
        axis.title.x = element_blank(),
        axis.text.x = element_text(size = 16,
                                   face = "bold"),
        plot.caption = element_text(size = 16, 
                                    hjust = -.3,
                                    face = "italic"),
        axis.text.y = element_text(size = 18,
                                   face = "bold")
        )

# ggsave("Graphs/Export_Wood.png", dpi = 1000)
```

















Historical stock price, retrieved from yahoo finance

```{r}
# lpx <- read.csv("lpx.csv")
# lpx <- lpx %>% mutate(Date = ymd(Date))
# 
# ggplot(lpx) + 
#   geom_line(aes(x = Date, y = Close, group = 1),
#             color = "#005581",
#             size = 2) +
#   ggtitle("LPX Stock Price") +
#   labs(caption = "Source: Yahoo Finance") +
#   scale_x_date(date_breaks = "1 year", 
#                date_labels = "%Y") +
#   scale_y_continuous(breaks = seq(15, 35, 5),
#                      limits = c(14, 35),
#                      labels = scales::dollar) +
#   theme_economist_white() +
#   theme(plot.title = element_text(size = 25, 
#                                   hjust = .5, 
#                                   face = "bold",
#                                   color = "#005581"),
#         axis.title.x = element_blank(),
#         axis.title.y = element_blank(),
#         axis.text.x = element_text(size = 18,
#                                    face = "bold"),
#         plot.caption = element_text(size = 18, 
#                                     hjust = -.1,
#                                     face = "italic"),
#         axis.text.y = element_text(size = 18,
#                                    face = "bold")
#         )

# ggsave("Present_Stock.png", dpi = 1000)
```

















